Influence of Connectivity on Dung Beetle Communities

### 2025-04-24 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
updates

@@

# Researchers today continue to search for strategies to mitigate the negative effects resulting from changes in landscape structure [@noh_forest_2022].

@@

All dung beetles were counted and identified to species.

 - We also dried and weighed individuals to estimate biomass  
 - what guides/keys did you do to ID?  
 - did you deposit vouchers and if so where are they available?

@@

_Don't have to describe these, just do it and report in results. this is just to remind us of what to do_

1. how many beetles total  
1. most common species overall.  
1. was. the same species the most common one in all habitats?  
1. were there any that were caught in all habitats? Any restricted to only one?  
1. any invasive / exotic species?  
1. Table: count by species by habitat.

@@

1. total number of beetles from total number of species: `r total_N` beetles from `r total_spp` species.
1. were all species found in all habitats? Were any species found in only 1 habitat?
1. Were all species found in all blocks? Were any restricted to only 1-2 blocks?
1. Were all species found in the matrix? (expect that so, since it is the 'baseline' or 'source' habitat)
1. Number of species in each functional group
1. most common 3-4 species: The `r how_many_common` most common species were \textit{`r most_common_spp[1,2]`} (N = `r most_common_spp[1,1]`), \textit{`r most_common_spp[2,2]`} (N = `r most_common_spp[2,1]`), and \textit{`r most_common_spp[3,2]`} (N = `r most_common_spp[3,1]`).
1. any rare species? 
1. any invasive / exotic species?

>>>>

# TO DO LIST

### Methods: 
1. add a few sentences on drying, keys used to ID, and depositing vouchers

### Analyses
1. Write a short paragraph on how you calculated and compared species richness and diversity (hill numbers, glmm). 
1. Write a short paragraph on how you calculated and compared functional diversity (how you measured it, how you compared it)

### Results
1. answer the overview questions, them stich them together into a paragraph
 - ~~any species restricted to 1-2 habitat types~~
 - Were all species found in all blocks? Were any restricted to only 1-2 blocks?
 - Were all species found in the matrix? (expect that so, since it is the 'baseline' or 'source' habitat)
 - Number of species in each functional group
 - ~~most common 3-4 species~~
 - any rare species? 
 - any invasive / exotic species?

### Figures

1. Figure of species richness results.
1. Figure of species diversity results.
1. Figure of biomass of different (R/T/D) functional groups.
1. Figure of abundance of individual species.
1. ~~Figure of the patch layout with pitfalls~~.

### Tables

1. ~~Table: count by species by habitat.~~
1. table: results of species richness analyses.
1. table: results of species diversity analyses.
1. table: results of functional diversity analyses.

### Misc.

1. Map of where field site is located.

1. Pictures of different species, sampling, field sites

@@

>_Researchers today continue to search for strategies to mitigate the negative effects resulting from changes in landscape structure [@noh_forest_2022]. _

@@

All dung beetles were counted and identified to species

 - We also dried and weighed individuals to estimate biomass  
 - what guides/keys did you do to ID?  
 - "Voucher specimens of species I collected will be deposited at the Florida State Collection of Arthropods" (https://thefsca.org/services/specimen-donations/)

@@

<!-- _Don't have to describe these, just do it and report in results. this is just to remind us of what to do_ -->

<!-- 1. how many beetles total   -->
<!-- 1. most common species overall.   -->
<!-- 1. was. the same species the most common one in all habitats?   -->
<!-- 1. were there any that were caught in all habitats? Any restricted to only one?   -->
<!-- 1. any invasive / exotic species?   -->
<!-- 1. Table: count by species by habitat.  -->

@@

1. total number of beetles from total number of species: `r total_N` beetles from `r total_spp` species.

1. All but four species species were found in every patch type. _Onthophagus concinnus_ was found in the matrix and winged patches, while _Onthophagus striatulus_ was found in matrix habitat and rectanular patches. _Geotrupes blackburnii_ and _Onthophagus tuberculifrons_ were the only species restricted to one patch type (winged and matrix, respectively).

1. Were all species found in all blocks? Were any restricted to only 1-2 blocks?
1. Were all species found in the matrix? (expect that so, since it is the 'baseline' or 'source' habitat)
1. Number of species in each functional group
1. most common 3-4 species: The `r how_many_common` most common species were \textit{`r most_common_spp[1,2]`} (N = `r most_common_spp[1,1]`), \textit{`r most_common_spp[2,2]`} (N = `r most_common_spp[2,1]`), and \textit{`r most_common_spp[3,2]`} (N = `r most_common_spp[3,1]`).
1. any rare species? 
1. any invasive / exotic species?
